---
title: "IATI Visualisation"
output: html_document
editor_options: 
  chunk_output_type: console
---



```{r developmenttest, include=FALSE, message=FALSE, warning=FALSE}
library(testthat) 
# Load already included functions
pkgload::load_all(export_all = FALSE)
```


# Using `iati::dataResult`

## show_indicators
    
 *  How much __indicators__ relate to target or baseline?
 
```{r function-show_indicators}
#' show_indicators
#' 
#' How much indicators evolve over time against thresholds?
#' 
#' @param year A numeric value corresponding to the first year of focus until the most recent year within the dataset.
#' @param programme_lab A character vector corresponding to the name of the programme.
#' @param iati_identifier_ops A character vector corresponding to the name of the operation.
#' @param ctr_name A character vector corresponding to the name of the country.
#' @param  result_type_name either  "Impact"  "Outcome" "Output" - default is  "Outcome" 
#' @param  type  "deviation" showing difference between target and actual - or 
#'               "progress"  showing difference between baseline and actual 
#' 
#' @import ggplot2
#' @import dplyr
#' @import scales
#' @import unhcrthemes
#' @importFrom stats reorder
#'
#' @export 
#' 
#' @return  a graph
show_indicators <- function(year, 
                        programme_lab = NULL, 
                        iati_identifier_ops = NULL, 
                        ctr_name = NULL ,
                       result_type_name = "Outcome",
                        type = "deviation") {
  
  
  # Check if only one argument is passed 
  if (!is.null(programme_lab) && !is.null(iati_identifier_ops)) {
    stop("Please pass only one of the arguments programme_lab or iati_identifier_ops.")
  } else if (!is.null(programme_lab) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments programme_lab or ctr_name.")
  } else if (!is.null(iati_identifier_ops) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments iati_identifier_ops or ctr_name.")
  }
  
  df <-  iati::dataResult |> 
         dplyr::left_join(iati::dataActivity, by= c("iati_identifier"))   
  
  if (!is.null(programme_lab)) {
    thisprogramme_lab <- programme_lab
    thisyear <-  year 
    thisresult_type_name <-  result_type_name
    df <- df |> 
      # levels(as.factor(df$result_type_name ))
      dplyr::filter( programmme_lab == thisprogramme_lab &
            year == thisyear & 
             result_type_name ==  thisresult_type_name)
  } else if (!is.null(iati_identifier_ops)) {
    thisiati_identifier_ops <- iati_identifier_ops
    thisyear <-  year 
    thisresult_type_name <-  result_type_name
    df <- df |> 
      dplyr::filter(iati_identifier_ops == thisiati_identifier_ops &
            year == thisyear & 
             result_type_name ==  thisresult_type_name)
  } else if (!is.null(ctr_name)) {
    thisctr_name <- ctr_name
    thisyear <-  year 
    thisresult_type_name <-  result_type_name
    df <- df |> 
      dplyr::filter( ctr_name == thisctr_name &
            year == thisyear & 
            result_type_name ==  thisresult_type_name)
  }
   
  ## in order to compare indictors alltogether in the same country, we need to normalise them
  ## one way is to compute the distance to the target...
  ## names(df)
  
  #table(df$result_indicator_ascending, useNA = "ifany")
  df1 <- df  |> 
    dplyr::select(result_type_name ,  result_title, 
                  indicator_measure_name, result_indicator_title,
                  
                  result_indicator_baseline_value, 
                  result_indicator_actual_value,
                  result_indicator_target_value,
                  result_indicator_target_value_1,
                  
                  result_indicator_baseline_location_ref, 
                  result_indicator_baseline_dimension_1,
                  result_indicator_baseline_dimension_value_1, 
                  result_indicator_baseline_dimension_2,
                  result_indicator_baseline_dimension_value_2,
                  result_indicator_ascending)  |>
  
    
     
      dplyr::mutate(  actual = as.numeric(result_indicator_actual_value),
                      baseline = as.numeric(result_indicator_baseline_value),
                      target = as.numeric(result_indicator_target_value), 
                      ## Reshape the indicator label... 
                      operation = as.character(glue::glue("{result_indicator_title} / {result_indicator_target_value_1}") ), 
                      # operation = as.character(glue::glue("{result_indicator_title} / {result_title} -
                      #                                        {result_indicator_target_value_1}") ),  
                      
              ## Calculating deviation to target        
                      deviation_actual_target =  round( ( actual - target ) / 
                                                           dplyr::if_else(target == 0, 1, target) * 
                                                           dplyr::if_else(target == 0, 1, 100) ,2 ),
               
                      ## Account for indicator direction
                      deviation_actual_target = dplyr::if_else(result_indicator_ascending == 0, 
                                                         deviation_actual_target * -1, 
                                                         deviation_actual_target),   
                      
                      deviation_color = dplyr::case_when(
                        deviation_actual_target >= -1     ~ "green",
                        deviation_actual_target < -1  & deviation_actual_target >= -15    ~ "orange",
                        deviation_actual_target < -15     ~ "red",  
                                                   TRUE ~ ""),
              ## Calculating progress to baseline..        
                      progress_baseline =  round( ( actual - baseline) / 
                                                           dplyr::if_else(baseline == 0, 1, baseline) * 
                                                           dplyr::if_else(baseline == 0, 1, 100)  ,2 ), 
                      ## Account for indicator direction
                      progress_baseline = dplyr::if_else(result_indicator_ascending == 0, 
                                                         progress_baseline * -1, 
                                                         progress_baseline),   
                      progress_color = dplyr::case_when(
                        progress_baseline >= -1     ~ "green",
                        progress_baseline < -1  & progress_baseline >= -15    ~ "orange",
                        progress_baseline < -15     ~ "red",  
                                                   TRUE ~ "")
              
              )    
  
  ### Type of chart to build...
  if(type == "deviation") {
    
      df1 <- df1 |> 
          ## Filter out - when no data...
          dplyr::filter (! (is.na(actual)))  |> 
          dplyr::filter (! (is.na(target)))  |> 
          dplyr::filter (! (is.nan(deviation_actual_target))) |>
          #dplyr::arrange(desc(actual))
          dplyr::group_by( result_indicator_title) |>
          dplyr::arrange(desc( actual), .by_group=TRUE )  |> 
          dplyr::ungroup(result_indicator_title)
     
          ## case there's no data at all
          if( nrow(df1) == 0) {
                info <-  paste0("No deviation - actual to target - \n comparative analysis \n  could be produced for \n",
                                result_type_name, " indicator values \n in ", 
                              programme_lab, ctr_name,iati_identifier_ops, " for year: ", year)
                p <- ggplot2::ggplot() +  
                     ggplot2::annotate("text",  x = 1, y = 1, size = 12,
                                          label = info ) +  
                     ggplot2::theme_void()
          
           } else if(nrow(df1)> 0) {
              ## and now the plot
              p <- ggplot2::ggplot(  data = df1) +
                ggplot2::coord_flip()  + 
                ggplot2::geom_col(   
                  ggplot2::aes(x = stats::reorder(operation, - deviation_actual_target),
                               y = deviation_actual_target,
                               fill = deviation_color ),
                            width = 0.7,
                            color = NA ) 
              
               p <-   p +
                ggplot2::scale_fill_manual(values = c( "red" = "#D3212C",   
                                              "orange" = "#FF980E",
                                              "green" = "#069C56")) +
                ggplot2::geom_text( 
                  ggplot2::aes(x = stats::reorder(operation, - deviation_actual_target), 
                               y = deviation_actual_target,
                               label = paste(round(deviation_actual_target, 1), " %") ),
                           #hjust = 1.5, 
                           size = 2.5,
                           color = "black")  +
                # scale_y_continuous( label = scales::label_percent(accuracy = 0,
                #                                    suffix = "%") ) +
                ggplot2::scale_y_continuous( label =  scales::label_number(accuracy = 1, 
                                                                  scale_cut = scales::cut_short_scale(),
                                                                  suffix = "%") )+
                ggplot2::scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 120)) +
                unhcrthemes::theme_unhcr(font_size = 18, 
                                         axis_text_size = 9,
                                         grid = "X", 
                                         axis = "y") +
                ggplot2::theme(  #axis.text.y = ggtext::element_markdown(),
                        legend.position = "none")+
                ggplot2::labs( x = "", y = "" ,
                      title = stringr::str_wrap( 
                        paste0( result_type_name, " Indicators | ", thisyear, " ", 
                                programme_lab, ctr_name,iati_identifier_ops ) ,
                        100),
                      subtitle = stringr::str_wrap( paste0( 
                        "Deviation between reported \"Actual\" value and programmatic \"Target\" (in %)" ) ,
                        110),
                      caption = stringr::str_wrap( 
                        "Source: Data published by UNHCR as part of the International Aid Transparency Initiative (IATI)" ,
                      110) )  
           }
    } else if( type == "progress")  {
      
      df1 <- df1 |> 
        ## Filter out - when no data...
        dplyr::filter (! (is.na(actual)))  |> 
        dplyr::filter (! (is.na(baseline)))  |> 
        dplyr::filter (! (is.nan(progress_baseline))) |>
        #dplyr::arrange(desc(actual))
        dplyr::group_by( result_indicator_title) |>
        dplyr::arrange(desc( actual), .by_group=TRUE )  |> 
        dplyr::ungroup(result_indicator_title)
 
        ## case there's no data at all
        if( nrow(df1) == 0) {
              info <- paste0("No progress - actual to baseline - \n comparative analysis \n  could be produced for \n",
                                  result_type_name, " indicator values \n in ", 
                                programme_lab, ctr_name,iati_identifier_ops, " for year: ", year)
              p <- ggplot2::ggplot() +  
                   ggplot2::annotate("text",  x = 1, y = 1, size = 12,
                                        label = info ) +  
                   ggplot2::theme_void()
        
         } else if(nrow(df1)> 0) {
            ## and now the plot
            p <-  ggplot2::ggplot(  data = df1) +
              ggplot2::coord_flip()  + 
              ggplot2::geom_col(   
                ggplot2::aes(x = stats::reorder(operation, - progress_baseline),
                             y = progress_baseline,
                             fill = deviation_color ),
                          width = 0.7,
                          color = NA ) 
            
             p <-   p +
              ggplot2::scale_fill_manual(values = c( "red" = "#D3212C",   
                                            "orange" = "#FF980E",
                                            "green" = "#069C56")) +
              ggplot2::geom_text( 
                ggplot2::aes(x = stats::reorder(operation, - progress_baseline), 
                             y = progress_baseline,
                             label = paste(round(progress_baseline, 1), " %") ),
                         #hjust = 1.5, 
                         size = 2.5,
                         color = "black")  +
              # scale_y_continuous( label = scales::label_percent(accuracy = 0,
              #                                    suffix = "%") ) +
              ggplot2::scale_y_continuous( label =  scales::label_number(accuracy = 1, 
                                                                scale_cut = scales::cut_short_scale(),
                                                                suffix = "%") )+
              ggplot2::scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 120)) +
              unhcrthemes::theme_unhcr(font_size = 18, 
                                       axis_text_size = 9,
                                       grid = "X", 
                                       axis = "y") +
              ggplot2::theme(  #axis.text.y = ggtext::element_markdown(),
                      legend.position = "none")+
              ggplot2::labs( x = "", y = "" ,
                    title = stringr::str_wrap( 
                      paste0( result_type_name, " Indicators | ", thisyear, " ", 
                              programme_lab, ctr_name,iati_identifier_ops ) ,
                      100),
                    subtitle = stringr::str_wrap( paste0( 
                      "Progress comparison between \"Actual\" reported value and their \"baseline\" (in %)" ) ,
                      110),
                    caption = stringr::str_wrap(
                      "Source: Data published by UNHCR as part of the International Aid Transparency Initiative (IATI)" ,
                    110) )  
             }
  }
  return(p)
    
}
```
  
```{r example-show_indicators, message=FALSE, warning=FALSE, fig.retina = 2, fig.width = 8,  fig.align = "center",  out.width = "90%"}
show_indicators(year = 2022,  
             ctr_name = "Brazil",
              result_type_name = "Outcome",
             type = "deviation"
             )
show_indicators(year = 2022,  
             ctr_name = "Brazil",
              result_type_name = "Impact",
             type = "deviation"
             )
show_indicators(year = 2019,  
             ctr_name = "Brazil",
              result_type_name = "Output",
             type = "deviation"
             )
show_indicators(year = 2022,  
             ctr_name = "Brazil",
              result_type_name = "Outcome",
             type = "progress"
             )
show_indicators(year = 2022,  
             ctr_name = "Brazil",
              result_type_name = "Impact",
             type = "progress"
             )
show_indicators(year = 2019,  
             ctr_name = "Brazil",
              result_type_name = "Output",
             type = "progress"
             )
```
  
```{r tests-show_indicators}
test_that("show_indicators works", {
  expect_true(inherits(show_indicators, "function")) 
})
```

## show_indicators_time
     
 
```{r function-show_indicators_time}
#' show_indicators_time
#' 
#' How much indicators evolve over time against thresholds?
#' 
#' @param year A numeric value corresponding to the first year of focus until the most recent year within the dataset.
#' @param ctr_name A character vector corresponding to the name of the country.
#' @param programme_lab A character vector corresponding to the name of the programme.
#' @param iati_identifier_ops A character vector corresponding to the name of the operation.
#' @param  result_type_name either  "Impact"  "Outcome" "Output" - default is  "Outcome" 
#' @param  type  "deviation" showing difference between target and actual - or 
#'               "progress"  showing difference between baseline and actual 
#' 
#' @import ggplot2
#' @import dplyr
#' @import scales
#' @import unhcrthemes
#' @importFrom stats reorder
#'
#' @export 
#' 
#' @return  a graph
show_indicators_time <- function(year, 
                        programme_lab = NULL, 
                        iati_identifier_ops = NULL, 
                        ctr_name = NULL ,
                       result_type_name = "Outcome",
                        type = "deviation") {
  
  
  # Check if only one argument is passed 
  if (!is.null(programme_lab) && !is.null(iati_identifier_ops)) {
    stop("Please pass only one of the arguments programme_lab or iati_identifier_ops.")
  } else if (!is.null(programme_lab) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments programme_lab or ctr_name.")
  } else if (!is.null(iati_identifier_ops) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments iati_identifier_ops or ctr_name.")
  }
  
  df <-  iati::dataResult |> 
         dplyr::left_join(iati::dataActivity, by= c("iati_identifier"))   
  
  if (!is.null(programme_lab)) {
    thisprogramme_lab <- programme_lab
    thisyear <-  year 
    thisresult_type_name <-  result_type_name
    df <- df |> 
      # levels(as.factor(df$result_type_name ))
      dplyr::filter( programmme_lab == thisprogramme_lab &
            year >= thisyear & 
             result_type_name ==  thisresult_type_name)  |>
      dplyr::left_join(iati::mapping_result, by= c("result_title"))  |>
      dplyr::distinct()
    
  } else if (!is.null(iati_identifier_ops)) {
    thisiati_identifier_ops <- iati_identifier_ops
    thisyear <-  year 
    thisresult_type_name <-  result_type_name
    df <- df |> 
      dplyr::filter(iati_identifier_ops == thisiati_identifier_ops &
            year >= thisyear & 
             result_type_name ==  thisresult_type_name)  |>
      dplyr::left_join(iati::mapping_result, by= c("result_title")) |>
      dplyr::distinct()
    
  } else if (!is.null(ctr_name)) {
    thisctr_name <- ctr_name
    thisyear <-  year 
    thisresult_type_name <-  result_type_name
    df <- df |> 
      dplyr::filter( ctr_name == thisctr_name &
            year >= thisyear & 
            result_type_name ==  thisresult_type_name)  |>
      dplyr::left_join(iati::mapping_result, by= c("result_title")) |>
      dplyr::distinct()
  }
   
  ## in order to compare indictors alltogether in the same country, we need to normalise them
  ## one way is to compute the distance to the target...
  ## names(df)
  
  #table(df$result_indicator_ascending, useNA = "ifany")
  df1 <- df  |> 
    dplyr::select(result_type_name ,  result_title, sector_rbm,
                  indicator_measure_name, result_indicator_title,
                  year,
                  
                  result_indicator_baseline_value, 
                  result_indicator_actual_value,
                  result_indicator_target_value,
                  result_indicator_target_value_1,
                  
                  result_indicator_baseline_location_ref, 
                  result_indicator_baseline_dimension_1,
                  result_indicator_baseline_dimension_value_1, 
                  result_indicator_baseline_dimension_2,
                  result_indicator_baseline_dimension_value_2,
                  result_indicator_ascending)  |>
  
     ## Quick fix in case ascending is not documented...
     dplyr::mutate(  result_indicator_ascending = dplyr::if_else( is.na(result_indicator_ascending), 
                                               
                                               "1", 
                                               result_indicator_ascending))   |>    
     
      dplyr::mutate(  actual = as.numeric(result_indicator_actual_value),
                      baseline = as.numeric(result_indicator_baseline_value),
                      target = as.numeric(result_indicator_target_value), 
                      ## Reshape the indicator label... 
                      operation = as.character(glue::glue("{result_indicator_title} / {result_indicator_target_value_1}") ), 
                      # operation = as.character(glue::glue("{result_indicator_title} / {result_title} -
                      #                                        {result_indicator_target_value_1}") ),  
                      
                      
              ## Calculating deviation to target        
                      deviation_actual_target =  round( ( actual - target ) / 
                                                           dplyr::if_else(target == 0, 1, target) * 
                                                           dplyr::if_else(target == 0, 1, 100) ,2 ),
               
                      ## Account for indicator direction
                      deviation_actual_target = dplyr::if_else(result_indicator_ascending == 0, 
                                                         deviation_actual_target * -1, 
                                                         deviation_actual_target),   
                      
                      deviation_color = dplyr::case_when(
                        deviation_actual_target >= -1     ~ "green",
                        deviation_actual_target < -1  & deviation_actual_target >= -15    ~ "orange",
                        deviation_actual_target < -15     ~ "red",  
                                                   TRUE ~ ""),
              ## Calculating progress to baseline..        
                      progress_baseline =  round( ( actual - baseline) / 
                                                           dplyr::if_else(baseline == 0, 1, baseline) * 
                                                           dplyr::if_else(baseline == 0, 1, 100)  ,2 ), 
                      ## Account for indicator direction
                      progress_baseline = dplyr::if_else(result_indicator_ascending == 0, 
                                                         progress_baseline * -1, 
                                                         progress_baseline),   
                      progress_color = dplyr::case_when(
                        progress_baseline >= -1     ~ "green",
                        progress_baseline < -1  & progress_baseline >= -15    ~ "orange",
                        progress_baseline < -15     ~ "red",  
                                                   TRUE ~ "")
              
              )    
  
  ### Type of chart to build...
  if(type == "deviation") {
    
      df1 <- df1 |> 
          ## Filter out - when no data...
          dplyr::filter (! (is.na(actual)))  |> 
          dplyr::filter (! (is.na(target)))  |> 
          dplyr::filter (! (is.nan(deviation_actual_target))) |>
          #dplyr::arrange(desc(actual))
          dplyr::group_by( result_indicator_title) |>
          dplyr::arrange(desc( actual), .by_group=TRUE )  |> 
          dplyr::ungroup(result_indicator_title)
     
          ## case there's no data at all
          if( nrow(df1) == 0) {
                info <-  paste0("No deviation - actual to target - \n comparative analysis \n  could be produced for \n",
                                result_type_name, " indicator values \n in ", 
                              programme_lab, ctr_name,iati_identifier_ops, " for year: ", year)
                p <- ggplot2::ggplot() +  
                     ggplot2::annotate("text",  x = 1, y = 1, size = 12,
                                          label = info ) +  
                     ggplot2::theme_void()
          
           } else if(nrow(df1)> 0) {
              ## and now the plot
              p <-  ggplot2::ggplot( df1, 
                 ggplot2::aes(x = year,
                          y = deviation_actual_target,
                   #shape = indicator_measure_name,
                   color = sector_rbm)) + 
  ggplot2::geom_jitter(position=position_jitter(0.2),
                       shape = 17,
                       size = 3) +
    ggplot2::stat_summary(fun.data=mean_sdl, #mult=1, 
                   geom="pointrange", color="grey", size = 1)   + 
    geom_hline(yintercept= 0, color="red") +
 # ggplot2::scale_color_viridis_d(option = "inferno", na.value = "grey50") + 
    ggplot2::scale_colour_brewer(palette = "Paired") +
  ggplot2::scale_y_continuous( label =  scales::label_number(accuracy = 1, 
                                                             scale_cut = scales::cut_short_scale(),
                                                             suffix = "%") )+
  ggplot2::scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 120)) +
  unhcrthemes::theme_unhcr(font_size = 22, 
                           axis_text_size = 9,
                           grid = "Y", 
                           axis = "y") +
    ggplot2::theme( legend.direction = "vertical",
                    legend.box = "horizontal",
                    legend.position = "right")+
  
  ggplot2::labs( x = "", y = "" ,
                 title = stringr::str_wrap( 
                   paste0( "Deviation Review | ", result_type_name, " Indicators   ", 
                           programme_lab, ctr_name,iati_identifier_ops ) ,
                   100), 
                 subtitle = stringr::str_wrap( paste0( 
                         "Between reported \"Actual\" value and programmatic \"Target\" (in %)" ) ,
                      110),
                 caption = stringr::str_wrap( 
                   "Source: Data published by UNHCR as part of the International Aid Transparency Initiative (IATI)" ,
                   110) )  
           }
    } else if( type == "progress")  {
      
      df1 <- df1 |> 
        ## Filter out - when no data...
        dplyr::filter (! (is.na(actual)))  |> 
        dplyr::filter (! (is.na(baseline)))  |> 
        dplyr::filter (! (is.nan(progress_baseline))) |>
        #dplyr::arrange(desc(actual))
        dplyr::group_by( result_indicator_title) |>
        dplyr::arrange(desc( actual), .by_group=TRUE )  |> 
        dplyr::ungroup(result_indicator_title)
 
        ## case there's no data at all
        if( nrow(df1) == 0) {
              info <- paste0("No progress - actual to baseline - \n comparative analysis \n  could be produced for \n",
                                  result_type_name, " indicator values \n in ", 
                                programme_lab, ctr_name,iati_identifier_ops, " for year: ", year)
              p <- ggplot2::ggplot() +  
                   ggplot2::annotate("text",  x = 1, y = 1, size = 12,
                                        label = info ) +  
                   ggplot2::theme_void()
        
         } else if(nrow(df1)> 0) {
            ## and now the plot
            p <-  ggplot2::ggplot( df1, 
                 ggplot2::aes(x = year,
                          y = progress_baseline,
                   #shape = indicator_measure_name,
                   color = sector_rbm)) + 
        ggplot2::geom_jitter(position=position_jitter(0.2),
                             shape = 17,
                             size = 3) +
          ggplot2::stat_summary(fun.data=mean_sdl, #mult=1, 
                         geom="pointrange", color="grey", size = .3)   + 
          geom_hline(yintercept= 0, color="red") +
       # ggplot2::scale_color_viridis_d(option = "inferno", na.value = "grey50") + 
          ggplot2::scale_colour_brewer(palette = "Paired") +
        ggplot2::scale_y_continuous( label =  scales::label_number(accuracy = 1, 
                                                                   scale_cut = scales::cut_short_scale(),
                                                                   suffix = "%") )+
        ggplot2::scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 120)) +
        unhcrthemes::theme_unhcr(font_size = 22, 
                                 axis_text_size = 9,
                                 grid = "Y", 
                                 axis = "y") +
          ggplot2::theme( legend.direction = "vertical",
                          legend.box = "horizontal",
                          legend.position = "right")+
        
        ggplot2::labs( x = "", y = "" ,
                       title = stringr::str_wrap( 
                         paste0( "Progress Comparison | ", result_type_name, " Indicators   ", 
                                 programme_lab, ctr_name,iati_identifier_ops ) ,
                         100),
                subtitle = stringr::str_wrap( paste0( 
                      "Between \"Actual\" reported value and their \"baseline\" (in %)" ) ,
                         110),
                       caption = stringr::str_wrap( 
                         "Source: Data published by UNHCR as part of the International Aid Transparency Initiative (IATI)" ,
                         110) )  
             }
    } else if( type == "gap")  {
      
      df1 <- df1 |> 
        ## Attach the mapping for outcome indicator threshold
        dplyr::left_join(iati::mapping_indicator)
        
        ## Filter out - when no data...
        dplyr::filter (! (is.na(actual)))  |> 
        dplyr::filter (! (is.na(baseline)))  |> 
        dplyr::filter (! (is.nan(progress_baseline))) |>
        #dplyr::arrange(desc(actual))
        dplyr::group_by( result_indicator_title) |>
        dplyr::arrange(desc( actual), .by_group=TRUE )  |> 
        dplyr::ungroup(result_indicator_title)
 
        ## case there's no data at all
        if( nrow(df1) == 0) {
              info <- paste0("No gap analysis - actual to green threshold - \n comparative analysis \n  could be produced for \n",
                                  result_type_name, " indicator values \n in ", 
                                programme_lab, ctr_name,iati_identifier_ops, " for year: ", year)
              p <- ggplot2::ggplot() +  
                   ggplot2::annotate("text",  x = 1, y = 1, size = 12,
                                        label = info ) +  
                   ggplot2::theme_void()
        
         } else if(nrow(df1)> 0) {
            ## and now the plot
            p <-  ggplot2::ggplot( df1, 
                 ggplot2::aes(x = year,
                          y = progress_baseline,
                   #shape = indicator_measure_name,
                   color = sector_rbm)) + 
        ggplot2::geom_jitter(position=position_jitter(0.2),
                             shape = 17,
                             size = 3) +
          ggplot2::stat_summary(fun.data=mean_sdl, #mult=1, 
                         geom="pointrange", color="grey", size = .3)   + 
          geom_hline(yintercept= 0, color="red") +
       # ggplot2::scale_color_viridis_d(option = "inferno", na.value = "grey50") + 
          ggplot2::scale_colour_brewer(palette = "Paired") +
        ggplot2::scale_y_continuous( label =  scales::label_number(accuracy = 1, 
                                                                   scale_cut = scales::cut_short_scale(),
                                                                   suffix = "%") )+
        ggplot2::scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 120)) +
        unhcrthemes::theme_unhcr(font_size = 22, 
                                 axis_text_size = 9,
                                 grid = "Y", 
                                 axis = "y") +
          ggplot2::theme( legend.direction = "vertical",
                          legend.box = "horizontal",
                          legend.position = "right")+
        
        ggplot2::labs( x = "", y = "" ,
                       title = stringr::str_wrap( 
                         paste0( "Progress Comparison | ", result_type_name, " Indicators   ", 
                                 programme_lab, ctr_name,iati_identifier_ops ) ,
                         100),
                subtitle = stringr::str_wrap( paste0( 
                      "Between \"Actual\" reported value and their \"baseline\" (in %)" ) ,
                         110),
                       caption = stringr::str_wrap( 
                         "Source: Data published by UNHCR as part of the International Aid Transparency Initiative (IATI)" ,
                         110) )  
             }
  }
  
  
  return(p)
    
}
```
  
```{r example-show_indicators_time, message=FALSE, warning=FALSE, fig.retina = 2, fig.width = 8,  fig.align = "center",  out.width = "90%"}
show_indicators_time(year = 2020,  
             ctr_name = "Brazil",
              result_type_name = "Outcome",
             type = "deviation"
             )
show_indicators_time(year =  2020, 
             ctr_name = "Brazil",
              result_type_name = "Impact",
             type = "deviation"
             )
show_indicators_time(year =  2020,  
             ctr_name = "Brazil",
              result_type_name = "Output",
             type = "deviation"
             )
show_indicators_time(year =  2020, 
             ctr_name = "Brazil",
              result_type_name = "Outcome",
             type = "progress"
             )
show_indicators_time(year =  2020, 
             ctr_name = "Brazil",
              result_type_name = "Impact",
             type = "progress"
             )
show_indicators_time(year =  2020, 
             ctr_name = "Brazil",
              result_type_name = "Output",
             type = "progress"
             )
```
  
```{r tests-show_indicators_time}
test_that("show_indicators_time works", {
  expect_true(inherits(show_indicators_time, "function")) 
})
```
  

# Using `iati::dataSector`

## show_sectors

 *  What are the __most funded sectors__ per country (Expenditure evolution per impact /outcome area)?  
    
```{r function-show_sectors}
#' show_sectors
#' 
#' @description  What are the most funded sectors per country (Expenditure evolution per impact /outcome area)?  
#' 
#' @param year A numeric value or a list of value.
#' @param programme_lab A character vector corresponding to the name of the programme.
#' @param iati_identifier_ops A character vector corresponding to the name of the operation.
#' @param ctr_name A character vector corresponding to the name of the country.
#' @param sector_vocabulary_name sector_vocabulary
#' 
#' @import ggplot2
#' @import dplyr
#' @import scales
#' @import unhcrthemes
#' @importFrom stats reorder
#'
#' @export 
#' @return  a graph
show_sectors <- function(year, 
                         programme_lab = NULL, 
                         iati_identifier_ops = NULL, 
                         ctr_name = NULL,
                         sector_vocabulary_name = "Reporting Organisation 2"){
  # Check if only one argument is passed 
  if (!is.null(programme_lab) && !is.null(iati_identifier_ops)) {
    stop("Please pass only one of the arguments programme_lab or iati_identifier_ops.")
  } else if (!is.null(programme_lab) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments programme_lab or ctr_name.")
  } else if (!is.null(iati_identifier_ops) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments iati_identifier_ops or ctr_name.")
  }
  
  # Join dataActivity and dataSector on iati_identifier 
  df <- iati::dataSector |>
    dplyr::left_join(iati::dataActivity,  by = c("iati_identifier"))
  
  if (!is.null(programme_lab)) {
    thisprogramme_lab <- programme_lab
    thisyear <- year
    thissector_vocabulary <- sector_vocabulary
    df <- df |> 
      dplyr::mutate(year = factor(year)) |>
      dplyr::filter(programmme_lab == thiprogramme_lab &
            year %in% thisyear & 
            sector_vocabulary_name ==  thissector_vocabulary_name)
  } else if (!is.null(iati_identifier_ops)) {
    thisiati_identifier_ops <- iati_identifier_ops
    thisyear <- year
    thissector_vocabulary_name <- sector_vocabulary_name
    df <- df |> 
      dplyr::mutate(year = factor(year)) |>
      dplyr::filter(iati_identifier_ops == thisiati_identifier_ops &
            year %in%  thisyear & 
            sector_vocabulary_name ==  thissector_vocabulary_name)
  } else if (!is.null(ctr_name)) {
    thisctr_name <- ctr_name
    thisyear <- year
    thissector_vocabulary_name <- sector_vocabulary_name
    df <- df |> 
      dplyr::mutate(year = factor(year)) |>
      dplyr::filter(ctr_name == thisctr_name &
            year %in% thisyear & 
            sector_vocabulary_name ==  thissector_vocabulary_name)
  }
  
  df <- df |> 
    dplyr::group_by(sector_desc, year) |> 
    dplyr::summarise(sector_pct = mean( as.numeric(sector_pct)) ) |> 
   # dplyr::summarise(sector_pct = sum(sector_pct, na.rm = TRUE)/sum(df$sector_pct, na.rm = TRUE)*100) |> 
  #  top_n(5, wt = sector_pct) |> 
    dplyr::mutate(sector_desc = as.factor(sector_desc))
  

  p <-  ggplot2::ggplot(data = df, 
                        ggplot2::aes(x = stats::reorder(sector_desc, sector_pct),
                                 y = sector_pct
                                 )) +
   # unhcrthemes::theme_unhcr(grid = TRUE, axis = "Y", axis_title = "Sector Percentage") +
    unhcrthemes::theme_unhcr(grid = "X", axis = "y", axis_title = "X", font_size = 18) +
    
    ggplot2::geom_bar(stat = "identity", fill = "#0072BC") +
    ggplot2::coord_flip()+
    ggplot2::facet_wrap( ggplot2::vars(year)) +
    ggplot2::scale_fill_viridis_d(option = "inferno", na.value = "grey50") +
    ggplot2::scale_y_continuous(expand = ggplot2::expansion(mult = c(0, .1)), labels = scales::label_number(scale_cut = scales::cut_short_scale())) +
    ggplot2::labs(title = "Resource Allocation per Sectors (%)", 
        subtitle = paste0("Recorded in ", programme_lab, ctr_name,iati_identifier_ops,
                          " based on vocabulary: ", sector_vocabulary_name),          
         x = "Sectors", y = "% of Total Funding", 
         caption = "Source: Data published by UNHCR as part of the International Aid Transparency Initiative (IATI)") 

    
 
  return(p)
}
```
  
```{r example-show_sectors, message=FALSE, warning=FALSE, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center",  out.width = "90%"}
knitr::kable( iati::dataSector |> 
                dplyr::select( sector_vocabulary_name, sector_vocabulary_description) |>
                dplyr::distinct() |>
                dplyr::filter(!(is.na(sector_vocabulary_name))))
show_sectors(
  year =  c(2020, 2021, 2022), 
  ctr_name = "Brazil",
  sector_vocabulary_name = "Reporting Organisation")
show_sectors(
  year = 2022, 
  ctr_name = "Brazil",
  sector_vocabulary_name = "Reporting Organisation 2")
show_sectors(
  year = c(2020, 2021, 2022),  
  ctr_name = "Brazil",
  sector_vocabulary_name = "Reporting Organisation 2")
show_sectors(
  year = c(2017,2018,2019,2020,2021, 2022), 
  ctr_name = "Brazil",
  sector_vocabulary_name = "Humanitarian Global Clusters (Inter-Agency Standing Committee)")
show_sectors(
  year = c(2017,2018,2019,2020,2021, 2022), 
  ctr_name = "Brazil",
  sector_vocabulary_name = "OECD DAC CRS Purpose Codes (5 digit)")
```
  
```{r tests-show_sectors}
test_that("show_sectors works", {
  expect_true(inherits(show_sectors, "function")) 
})
```

## show_goal_sdg
    
```{r function-show_goal_sdg}
#' show_goal_sdg
#' 
#' @description Show resource allocation in line with SDG goal
#' @param year A numeric value or a list of value.
#' @param programme_lab A character vector corresponding to the name of the programme.
#' @param iati_identifier_ops A character vector corresponding to the name of the operation.
#' @param ctr_name A character vector corresponding to the name of the country. 
#' 
#' @import ggplot2
#' @import dplyr
#' @import scales
#' @import unhcrthemes
#' @importFrom stats reorder
#'
#' @export 
#' @return  a graph
show_goal_sdg <- function(year, 
                         programme_lab = NULL, 
                         iati_identifier_ops = NULL, 
                         ctr_name = NULL ){
  # Check if only one argument is passed 
  if (!is.null(programme_lab) && !is.null(iati_identifier_ops)) {
    stop("Please pass only one of the arguments programme_lab or iati_identifier_ops.")
  } else if (!is.null(programme_lab) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments programme_lab or ctr_name.")
  } else if (!is.null(iati_identifier_ops) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments iati_identifier_ops or ctr_name.")
  }
  
  # Join dataActivity and dataSector on iati_identifier 
  df <- iati::dataSector |>
    dplyr::left_join(iati::dataActivity,  by = c("iati_identifier"))
  
  if (!is.null(programme_lab)) {
    thisprogramme_lab <- programme_lab
    thisyear <- year 
    df <- df |> 
      dplyr::mutate(year = factor(year)) |>
      dplyr::filter(programmme_lab == thiprogramme_lab &
            year %in% thisyear & 
            sector_vocabulary_name ==  "Reporting Organisation 2") |>
      dplyr::left_join(iati::mapping_sector, by= c("sector_desc")) |>
      dplyr::left_join(iati::mapping_sdg, by= c("sector_rbm" = "area")) 
      
  } else if (!is.null(iati_identifier_ops)) {
    thisiati_identifier_ops <- iati_identifier_ops
    thisyear <- year 
    df <- df |> 
      dplyr::mutate(year = factor(year)) |>
      dplyr::filter(iati_identifier_ops == thisiati_identifier_ops &
            year %in%  thisyear & 
            sector_vocabulary_name ==  "Reporting Organisation 2") |>
      dplyr::left_join(iati::mapping_sector, by= c("sector_desc"))|>
      dplyr::left_join(iati::mapping_sdg, by= c("sector_rbm" = "area")) 
  } else if (!is.null(ctr_name)) {
    thisctr_name <- ctr_name
    thisyear <- year 
    df <- df |> 
      dplyr::mutate(year = factor(year)) |>
      dplyr::filter(ctr_name == thisctr_name &
            year %in% thisyear & 
            sector_vocabulary_name == "Reporting Organisation 2") |>
      dplyr::left_join(iati::mapping_sector, by= c("sector_desc"))|>
      dplyr::left_join(iati::mapping_sdg, by= c("sector_rbm" = "area")) 
  }
  
  df <- df |> 
    dplyr::group_by(sector_desc, sector_rbm,sdg, year) |> 
    dplyr::summarise(sector_pct = mean( as.numeric(sector_pct)) ) |> 
    dplyr::group_by( sdg, year) |> 
    dplyr::summarise(sector_pct = sum(sector_pct, rm.na = TRUE))  |> 
   # dplyr::summarise(sector_pct = sum(sector_pct, na.rm = TRUE)/sum(df$sector_pct, na.rm = TRUE)*100) |> 
  #  top_n(5, wt = sector_pct) |> 
    dplyr::mutate(sdg = as.factor(sdg))
  
  
  ## Now joining budget & Expenditure to make the chart more informative...
   df_bud <-  iati::dataTransaction |> 
         dplyr::left_join(iati::dataActivity, by= c("iati_identifier"))  
  
  if (!is.null(programme_lab)) {
    thisprogramme_lab <- programme_lab
    thisyear <-  year 
   df_bud <- df_bud |> 
      # levels(as.factor(df$programmme_lab))
      dplyr::filter( programmme_lab == thisprogramme_lab &
            year  %in% thisyear & 
             transaction_type_name ==  "Expenditure")
  } else if (!is.null(iati_identifier_ops)) {
    thisiati_identifier_ops <- iati_identifier_ops
    thisyear <-  year 
   df_bud <- df_bud |> 
      dplyr::filter(iati_identifier_ops == thisiati_identifier_ops &
            year  %in% thisyear & 
             transaction_type_name ==  "Expenditure")
  } else if (!is.null(ctr_name)) {
    thisctr_name <- ctr_name
    thisyear <-  year 
    df_bud <- df_bud |> 
      dplyr::filter( ctr_name == thisctr_name &
            year    %in% thisyear & 
             transaction_type_name ==  "Expenditure")
  }
  
   df_bud2 <-  df_bud  |> 
        dplyr::group_by(iati_identifier, year) |>
        dplyr::summarise(transaction_value= sum(transaction_value, na.rm = TRUE)) |>
        dplyr::left_join(iati::dataBudget |> 
                          dplyr::mutate(budget_value= as.numeric(budget_value)) |>
                          dplyr::group_by(iati_identifier) |>
                          dplyr::summarise(budget_value= sum(budget_value, na.rm = TRUE))  
                            , by= c("iati_identifier"))  |>
     dplyr::select(iati_identifier, year,budget_value,   transaction_value ) |>
     dplyr::mutate( year2 = glue::glue('{year} - Bud:{scales::label_number(accuracy = .2, scale_cut = scales::cut_short_scale())(budget_value)}$/ Exp:{scales::label_number(accuracy = .2, scale_cut = scales::cut_short_scale())(transaction_value)}$  '))
   
   df <- df |>
         dplyr::left_join(df_bud2, by = c("year"))
   
  

  p <-  ggplot2::ggplot(data = df, 
                        ggplot2::aes(x = stats::reorder(sdg, sector_pct),
                                 y = sector_pct
                                 )) +
   # unhcrthemes::theme_unhcr(grid = TRUE, axis = "Y", axis_title = "Sector Percentage") +
    unhcrthemes::theme_unhcr(grid = "X", axis = "y", axis_title = "X", font_size = 18) +
    
    ggplot2::geom_bar(stat = "identity", fill = "#0072BC") +
    ggplot2::coord_flip()+
    ggplot2::facet_wrap( ggplot2::vars(year2), labeller = labeller(year2 = ggplot2::label_wrap_gen(5))) +
    ggplot2::scale_fill_viridis_d(option = "inferno", na.value = "grey50") +
    ggplot2::scale_y_continuous(expand = ggplot2::expansion(mult = c(0, .1)), labels = scales::label_number(scale_cut = scales::cut_short_scale())) +
    ggplot2::labs(title = "Resource Allocation per SDG (%)", 
        subtitle = paste0("Recorded in ", programme_lab, ctr_name,iati_identifier_ops,
                          "  "),          
         x = "Sectors", y = "% of Total Funding", 
         caption = "Source: Data published by UNHCR as part of the International Aid Transparency Initiative (IATI). UNHCR budget is needs-based. It represents the total amount of money that would be required were UNHCR to meet all of the needs that it is seeking to address.") 

  return(p)
}
```
  
```{r example-show_goal_sdg, message=FALSE, warning=FALSE, fig.retina = 2, fig.width = 8,  fig.align = "center",  out.width = "90%"}
show_goal_sdg(year =  c(  2020, 2021, 2022), 
             ctr_name = "Brazil")
```
  
```{r tests-show_goal_sdg}
test_that("show_goal_sdg works", {
  expect_true(inherits(show_goal_sdg, "function")) 
})
```
  

## show_outcome_rbm
    
```{r function-show_outcome_rbm}

#' show_outcome_rbm
#' 
#' @description  What are the most funded sectors per country based on new RBM framework.
#'   The activities that UNHCR plans and undertakes around the world are described
#'    under 16 "Outcome Areas".   
#' 
#' @param year A numeric value or a list of value.
#' @param programme_lab A character vector corresponding to the name of the programme.
#' @param iati_identifier_ops A character vector corresponding to the name of the operation.
#' @param ctr_name A character vector corresponding to the name of the country. 
#' 
#' @import ggplot2
#' @import dplyr
#' @import scales
#' @import unhcrthemes
#' @importFrom stats reorder
#'
#' @export 
#' @return  a graph
show_outcome_rbm <- function(year, 
                         programme_lab = NULL, 
                         iati_identifier_ops = NULL, 
                         ctr_name = NULL ){
  # Check if only one argument is passed 
  if (!is.null(programme_lab) && !is.null(iati_identifier_ops)) {
    stop("Please pass only one of the arguments programme_lab or iati_identifier_ops.")
  } else if (!is.null(programme_lab) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments programme_lab or ctr_name.")
  } else if (!is.null(iati_identifier_ops) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments iati_identifier_ops or ctr_name.")
  }
  
  # Join dataActivity and dataSector on iati_identifier 
  df <- iati::dataSector |>
    dplyr::left_join(iati::dataActivity,  by = c("iati_identifier"))
  
  if (!is.null(programme_lab)) {
    thisprogramme_lab <- programme_lab
    thisyear <- year 
    df <- df |> 
      dplyr::mutate(year = factor(year)) |>
      dplyr::filter(programmme_lab == thiprogramme_lab &
            year %in% thisyear & 
            sector_vocabulary_name ==  "Reporting Organisation 2") |>
      dplyr::left_join(iati::mapping_sector, by= c("sector_desc"))
  } else if (!is.null(iati_identifier_ops)) {
    thisiati_identifier_ops <- iati_identifier_ops
    thisyear <- year 
    df <- df |> 
      dplyr::mutate(year = factor(year)) |>
      dplyr::filter(iati_identifier_ops == thisiati_identifier_ops &
            year %in%  thisyear & 
            sector_vocabulary_name ==  "Reporting Organisation 2") |>
      dplyr::left_join(iati::mapping_sector, by= c("sector_desc"))
  } else if (!is.null(ctr_name)) {
    thisctr_name <- ctr_name
    thisyear <- year 
    df <- df |> 
      dplyr::mutate(year = factor(year)) |>
      dplyr::filter(ctr_name == thisctr_name &
            year %in% thisyear & 
            sector_vocabulary_name == "Reporting Organisation 2") |>
      dplyr::left_join(iati::mapping_sector, by= c("sector_desc"))
  }
  
  df <- df |> 
    dplyr::group_by(sector_desc, sector_rbm, year) |> 
    dplyr::summarise(sector_pct = mean( as.numeric(sector_pct)) ) |> 
    dplyr::group_by( sector_rbm, year) |> 
    dplyr::summarise(sector_pct = sum(sector_pct, rm.na = TRUE))  |> 
   # dplyr::summarise(sector_pct = sum(sector_pct, na.rm = TRUE)/sum(df$sector_pct, na.rm = TRUE)*100) |> 
  #  top_n(5, wt = sector_pct) |> 
    dplyr::mutate(sector_rbm = as.factor(sector_rbm))
  
  
  ## Now joining budget & Expenditure to make the chart more informative...
   df_bud <-  iati::dataTransaction |> 
         dplyr::left_join(iati::dataActivity, by= c("iati_identifier"))  
  
  if (!is.null(programme_lab)) {
    thisprogramme_lab <- programme_lab
    thisyear <-  year 
   df_bud <- df_bud |> 
      # levels(as.factor(df$programmme_lab))
      dplyr::filter( programmme_lab == thisprogramme_lab &
            year  %in% thisyear & 
             transaction_type_name ==  "Expenditure")
  } else if (!is.null(iati_identifier_ops)) {
    thisiati_identifier_ops <- iati_identifier_ops
    thisyear <-  year 
   df_bud <- df_bud |> 
      dplyr::filter(iati_identifier_ops == thisiati_identifier_ops &
            year  %in% thisyear & 
             transaction_type_name ==  "Expenditure")
  } else if (!is.null(ctr_name)) {
    thisctr_name <- ctr_name
    thisyear <-  year 
    df_bud <- df_bud |> 
      dplyr::filter( ctr_name == thisctr_name &
            year    %in% thisyear & 
             transaction_type_name ==  "Expenditure")
  }
  
   df_bud2 <-  df_bud  |> 
        dplyr::group_by(iati_identifier, year) |>
        dplyr::summarise(transaction_value= sum(transaction_value, na.rm = TRUE)) |>
        dplyr::left_join(iati::dataBudget |> 
                          dplyr::mutate(budget_value= as.numeric(budget_value)) |>
                          dplyr::group_by(iati_identifier) |>
                          dplyr::summarise(budget_value= sum(budget_value, na.rm = TRUE))  
                            , by= c("iati_identifier"))  |>
     dplyr::select(iati_identifier, year,budget_value,   transaction_value ) |>
     dplyr::mutate( year2 = glue::glue('{year}  Bud: {scales::label_number(accuracy = .2, scale_cut = scales::cut_short_scale())(budget_value)}$/ Exp: {scales::label_number(accuracy = .2, scale_cut = scales::cut_short_scale())(transaction_value)}$  '))
   
   df <- df |>
         dplyr::left_join(df_bud2, by = c("year"))
   
  

  p <-  ggplot2::ggplot(data = df, 
                        ggplot2::aes(x = stats::reorder(sector_rbm, sector_pct),
                                 y = sector_pct
                                 )) +
   # unhcrthemes::theme_unhcr(grid = TRUE, axis = "Y", axis_title = "Sector Percentage") +
    unhcrthemes::theme_unhcr(grid = "X", axis = "y", axis_title = "X", font_size = 18) +
    
    ggplot2::geom_bar(stat = "identity", fill = "#0072BC") +
    ggplot2::coord_flip()+
    ggplot2::facet_wrap( ggplot2::vars(year2), labeller = labeller(year2 = ggplot2::label_wrap_gen(5))) +
    ggplot2::scale_fill_viridis_d(option = "inferno", na.value = "grey50") +
    ggplot2::scale_y_continuous(expand = ggplot2::expansion(mult = c(0, .1)), labels = scales::label_number(scale_cut = scales::cut_short_scale())) +
    ggplot2::labs(title = "Resource Allocation per Outcome (%)", 
        subtitle = paste0("Recorded in ", programme_lab, ctr_name,iati_identifier_ops,
                          " based on UNHCR Results Framework "),          
         x = "Sectors", y = "% of Total Funding", 
         caption = "Source: Data published by UNHCR as part of the International Aid Transparency Initiative (IATI). UNHCR budget is needs-based. It represents the total amount of money that would be required were UNHCR to meet all of the needs that it is seeking to address.") 

  return(p)
}
```
  
```{r example-show_outcome_rbm, message=FALSE, warning=FALSE, fig.retina = 2, fig.width = 8,  fig.align = "center",  out.width = "90%"}
show_outcome_rbm( year =  c(  2020, 2021, 2022), 
             ctr_name = "Brazil")
```
  
```{r tests-show_outcome_rbm}
test_that("show_outcome_rbm works", {
  expect_true(inherits(show_outcome_rbm, "function")) 
})
```
     
 


# Using `iati::dataBudget`

## show_expenditure

 *  How much __expenditures compare to the initial budget__ (potentially weighted by # )?   
    
```{r function-show_expenditure}
#' show_expenditure
#' 
#' How much expenditures compare to the initial budget (potentially weighted by #)?   
#' 
#' @param year A numeric value corresponding to the first year of focus until the most recent year within the dataset.
#' @param programme_lab A character vector corresponding to the name of the programme.
#' @param iati_identifier_ops A character vector corresponding to the name of the operation.
#' @param ctr_name A character vector corresponding to the name of the country.
#' @param weight_by list of population group to weight the budget - 
#'                   "refugees", "asylum_seekers",
#'                    "returned_refugees" "idps",
#'                    "returned_idps", "stateless", 
#'                    "ooc", "oip"  
#'                   default is null.
#' 
#' @import ggplot2
#' @import dplyr
#' @import tidyselect
#' @import scales
#' @import unhcrthemes
#' @import refugees
#'
#' @export 
#' @return  a graph
show_expenditure <- function(year, 
                        programme_lab = NULL, 
                        iati_identifier_ops = NULL, 
                        ctr_name = NULL ,
                        weight_by = NULL) {
  
  
  # Check if only one argument is passed 
  if (!is.null(programme_lab) && !is.null(iati_identifier_ops)) {
    stop("Please pass only one of the arguments programme_lab or iati_identifier_ops.")
  } else if (!is.null(programme_lab) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments programme_lab or ctr_name.")
  } else if (!is.null(iati_identifier_ops) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments iati_identifier_ops or ctr_name.")
  }
  
  df <-  iati::dataTransaction |> 
         dplyr::left_join(iati::dataActivity, by= c("iati_identifier"))  
  
  if (!is.null(programme_lab)) {
    thisprogramme_lab <- programme_lab
    thisyear <-  year 
    df <- df |> 
      # levels(as.factor(df$programmme_lab))
      dplyr::filter( programmme_lab == thisprogramme_lab &
            year >= thisyear & 
             transaction_type_name ==  "Expenditure")
  } else if (!is.null(iati_identifier_ops)) {
    thisiati_identifier_ops <- iati_identifier_ops
    thisyear <-  year 
    df <- df |> 
      dplyr::filter(iati_identifier_ops == thisiati_identifier_ops &
            year >= thisyear & 
             transaction_type_name ==  "Expenditure")
  } else if (!is.null(ctr_name)) {
    thisctr_name <- ctr_name
    thisyear <-  year 
    df <- df |> 
      dplyr::filter( ctr_name == thisctr_name &
            year >= thisyear & 
             transaction_type_name ==  "Expenditure")
  }
  
   df2 <-  df  |> 
        dplyr::group_by(iati_identifier, year) |>
        dplyr::summarise(transaction_value= sum(transaction_value, na.rm = TRUE)) |>
        dplyr::left_join(iati::dataBudget |> 
                          dplyr::mutate(budget_value= as.numeric(budget_value)) |>
                          dplyr::group_by(iati_identifier) |>
                          dplyr::summarise(budget_value= sum(budget_value, na.rm = TRUE))  
                            , by= c("iati_identifier"))  |>
     dplyr::select(iati_identifier, year,budget_value,   transaction_value )  
   
    # Error catching -- Check if we weight
    #weight_by <-  c("refugees", "oip") 
    #weight_by <-  c("refugees", "oidp")
   
    if (  !is.null(weight_by) &&  !all(weight_by %in% c("refugees", "asylum_seekers",
                                                   "returned_refugees", "idps",
                                                   "returned_idps", "stateless", 
                                                   "ooc", "oip"  ))  ) {
     stop("weight_by is used but the population filter is not correctly set up...\n
          it should be among: refugees, asylum_seekers, returned_refugees, idps,
          returned_idps, stateless,  ooc, oip")
    } 
   
   ## Calculate weight
   if (!is.null(weight_by) && !is.null(ctr_name) ) {
     ctrstat <- refugees::population |>
            dplyr::filter( year>= thisyear & 
                             coa_name == thisctr_name) |>
            dplyr::group_by(year, coa_name) |>
            dplyr::summarise(refugees = sum(refugees, na.rm = TRUE),
                             asylum_seekers = sum(asylum_seekers, na.rm = TRUE),
                              returned_refugees = sum(returned_refugees, na.rm = TRUE),
                              idps = sum(idps, na.rm = TRUE),
                              returned_idps = sum(returned_idps , na.rm = TRUE),
                              stateless = sum(stateless, na.rm = TRUE),
                              ooc = sum( ooc, na.rm = TRUE),
                              oip = sum(oip, na.rm = TRUE)) |>
            dplyr::select(year, coa_name, all_of(weight_by) ) |>
            dplyr::mutate(year = as.factor(year) ) |>
            dplyr::mutate( weight = rowSums(
                                   dplyr::across(tidyselect::where(is.numeric))))
     
      df2 <-  df2 |>
        dplyr::left_join(ctrstat |> 
                         dplyr::select(year, weight)   , by = c("year")) |>
        dplyr::mutate(budget_value = round(budget_value / weight,1),   
                      transaction_value = round(transaction_value  / weight,1))
     
    } 
   
 subtitt <- if( is.null(weight_by)) {
   paste0("In ", programme_lab, ctr_name,iati_identifier_ops, " recorded since ", year,"")
   } else {
   paste0("Weighted by total number of individual ", 
          paste(weight_by, collapse = ', '),
          " in ", 
          programme_lab, ctr_name,iati_identifier_ops, " as recorded since ", year,"")
     }
 
 
 p <- df2 |> 
#  dplyr::filter(transaction_value_USD  <= 1000000 & transaction_value_USD  > 1000) |> 
  ggplot2::ggplot(ggplot2::aes(x =  year, group = 1)) +
  ggplot2::geom_line(ggplot2::aes(y = budget_value,
                         color = "Budget"), linewidth = 1.5) +
  ggplot2::geom_line(ggplot2::aes(y =  transaction_value, 
                         color = "Expenditure"), linewidth = 1.5) +
  ggplot2::scale_color_manual(name = " ", 
                               values = c("Expenditure" = "#F592A0", "Budget" = "#00568D")) +
  ggplot2::scale_y_continuous(
   # expand = ggplot2::expansion(mult = c(0, .1)),
    labels = scales::label_number(scale_cut = scales::cut_short_scale())  ) +
#  scale_x_continuous(labels = scales::label_number(scale_cut = cut_short_scale())) +
 # ggplot2::facet_wrap(~ trans_year) +
  unhcrthemes::theme_unhcr(grid = "Y", axis = "X", 
                           axis_title = "X", font_size = 18,
                           legend = FALSE)+
  ggplot2::labs(
    title = paste0("<span style='color:\"#00568D\"'>Budget</span>  vs <span style='color:\"#F592A0\"'>Expenditure</span>  (in USD)"),
    subtitle = subtitt,
    x = "",
    y = "",
    caption = "Source: Data published by UNHCR as part of the International Aid Transparency Initiative (IATI). UNHCR budget is needs-based. It represents the total amount of money that would be required were UNHCR to meet all of the needs that it is seeking to address." ) 
 
  return(p)
}
```
  
```{r example-show_expenditure, message=FALSE, warning=FALSE, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center",  out.width = "90%"}
show_expenditure(year = 2018, 
             ctr_name = "Brazil")

show_expenditure(year = 2018, 
             ctr_name = "Brazil",
             weight_by = c("refugees", "oip"))

```
  
```{r tests-show_expenditure}
test_that("show_expenditure works", {
  expect_true(inherits(show_expenditure, "function")) 
})
```


## show_budget_gap
    
```{r function-show_budget_gap}
#' show_budget_gap
#' 
#' UNHCR budgets are needs-based: it represents the total amount
#' of money that would be required were UNHCR to meet all of the needs that it is seeking to address.
#' 
#' @param year A numeric value corresponding to the first year of focus until the most recent year within the dataset.
#' @param programme_lab A character vector corresponding to the name of the programme.
#' @param iati_identifier_ops A character vector corresponding to the name of the operation.
#' @param ctr_name A character vector corresponding to the name of the country.
#' @param weight_by list of population group to weight the budget - 
#'                   "refugees", "asylum_seekers",
#'                    "returned_refugees" "idps",
#'                    "returned_idps", "stateless", 
#'                    "ooc", "oip"  
#'                   default is null.
#' 
#' @import ggplot2
#' @import dplyr
#' @import tidyselect
#' @import scales
#' @import unhcrthemes 
#'
#' @export 
#' @return  a graph
show_budget_gap <- function(year, 
                        programme_lab = NULL, 
                        iati_identifier_ops = NULL, 
                        ctr_name = NULL ,
                        weight_by = NULL ) {
  
  
  # Check if only one argument is passed 
  if (!is.null(programme_lab) && !is.null(iati_identifier_ops)) {
    stop("Please pass only one of the arguments programme_lab or iati_identifier_ops.")
  } else if (!is.null(programme_lab) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments programme_lab or ctr_name.")
  } else if (!is.null(iati_identifier_ops) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments iati_identifier_ops or ctr_name.")
  }
  
  df <-  iati::dataTransaction |> 
         dplyr::left_join(iati::dataActivity, by= c("iati_identifier"))  
  
  if (!is.null(programme_lab)) {
    thisprogramme_lab <- programme_lab
    thisyear <-  year 
    df <- df |> 
      # levels(as.factor(df$programmme_lab))
      dplyr::filter( programmme_lab == thisprogramme_lab &
            year >= thisyear & 
             transaction_type_name ==  "Expenditure")
  } else if (!is.null(iati_identifier_ops)) {
    thisiati_identifier_ops <- iati_identifier_ops
    thisyear <-  year 
    df <- df |> 
      dplyr::filter(iati_identifier_ops == thisiati_identifier_ops &
            year >= thisyear & 
             transaction_type_name ==  "Expenditure")
  } else if (!is.null(ctr_name)) {
    thisctr_name <- ctr_name
    thisyear <-  year 
    df <- df |> 
      dplyr::filter( ctr_name == thisctr_name &
            year >= thisyear & 
             transaction_type_name ==  "Expenditure")
  }
  
   df2 <-  df  |> 
        dplyr::group_by(iati_identifier, year) |>
        dplyr::summarise(transaction_value= sum(transaction_value, na.rm = TRUE)) |>
        dplyr::left_join(iati::dataBudget |> 
                          dplyr::mutate(budget_value= as.numeric(budget_value)) |>
                          dplyr::group_by(iati_identifier) |>
                          dplyr::summarise(budget_value= sum(budget_value, na.rm = TRUE))  
                            , by= c("iati_identifier"))  |>
     dplyr::select(iati_identifier, year,budget_value,   transaction_value )  |>
     dplyr::mutate(budget_gap = (budget_value - transaction_value) / budget_value *100) 
   
 
   
    if (  !is.null(weight_by) &&  !all(weight_by %in% c("refugees", "asylum_seekers",
                                                   "returned_refugees", "idps",
                                                   "returned_idps", "stateless", 
                                                   "ooc", "oip"  ))  ) {
     stop("weight_by is used but the population filter is not correctly set up...\n
          it should be among: refugees, asylum_seekers, returned_refugees, idps,
          returned_idps, stateless,  ooc, oip")
    } 
   
   ## Calculate weight
   if (!is.null(weight_by) && !is.null(ctr_name) ) {
     ctrstat <- refugees::population |>
            dplyr::filter( year>= thisyear & 
                             coa_name == thisctr_name) |>
            dplyr::group_by(year, coa_name) |>
            dplyr::summarise(refugees = sum(refugees, na.rm = TRUE),
                             asylum_seekers = sum(asylum_seekers, na.rm = TRUE),
                              returned_refugees = sum(returned_refugees, na.rm = TRUE),
                              idps = sum(idps, na.rm = TRUE),
                              returned_idps = sum(returned_idps , na.rm = TRUE),
                              stateless = sum(stateless, na.rm = TRUE),
                              ooc = sum( ooc, na.rm = TRUE),
                              oip = sum(oip, na.rm = TRUE)) |>
            dplyr::select(year, coa_name, all_of(weight_by) ) |>
            dplyr::mutate(year = as.factor(year) ) |>
            dplyr::mutate( weight = rowSums(
                                   dplyr::across(tidyselect::where(is.numeric))))
     
      df2 <-  df2 |>
        dplyr::left_join(ctrstat |> 
                         dplyr::select(year, weight)   , by = c("year")) |>
        dplyr::mutate(budget_value = round(budget_value / weight,1),   
                      transaction_value = round(transaction_value  / weight,1))
      df2 <-  df2 |>
       dplyr::mutate(budget_gap2 = (budget_value - transaction_value) / budget_value *100) 
     
    } 
   
 subtitt <- if( is.null(weight_by)) {
   paste0("In ", programme_lab, ctr_name,iati_identifier_ops, " recorded since ", year,"")
   } else {
   paste0("Weighted by total number of individual ", 
          paste(weight_by, collapse = ', '),
          " in ", 
          programme_lab, ctr_name,iati_identifier_ops, " as recorded since ", year,"")
     }
 
   
   
 
 p <- df2 |> 
#  dplyr::filter(transaction_value_USD  <= 1000000 & transaction_value_USD  > 1000) |> 
  ggplot2::ggplot(ggplot2::aes(x =  year, group = 1)) +
  ggplot2::geom_line(ggplot2::aes(y = budget_gap,
                         color = "Budget"),
                     linewidth = 1.5,
                     color = "#F592A0") +  
  ggplot2::scale_y_continuous(  limits=c(0,100)) +
  # ggplot2::scale_y_continuous(
  #   #expand = ggplot2::expansion(mult = c(0, .1)),
  #   labels = scales::label_number(scale_cut = scales::cut_short_scale())  ) +
#  scale_x_continuous(labels = scales::label_number(scale_cut = cut_short_scale())) +
 # ggplot2::facet_wrap(~ trans_year) +
  unhcrthemes::theme_unhcr(grid = "Y", axis = "X", 
                           axis_title = "X", font_size = 18,
                           legend = FALSE)+
  ggplot2::labs(
    title = paste0( "Budget Gap  (in %)"),
    subtitle =   subtitt ,
    x = "",
    y = "",
    caption = "Source: Data published by UNHCR as part of the International Aid Transparency Initiative (IATI). UNHCR budget is needs-based. It represents the total amount of money that would be required were UNHCR to meet all of the needs that it is seeking to address." ) 
 
  return(p)
    
}
```
  
```{r example-show_budget_gap, message=FALSE, warning=FALSE, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center",  out.width = "90%"}
show_budget_gap(year = 2018, 
             ctr_name = "Brazil")
show_budget_gap(year = 2018, 
             ctr_name = "Brazil",
             weight_by = c("refugees", "oip"))
```
  
```{r tests-show_budget_gap}
test_that("show_budget_gap works", {
  expect_true(inherits(show_budget_gap, "function")) 
})
```
  

# Using  `iati::dataTransaction`

## Show donors 
 
 *  Who are the __main donors by country__ in terms of transaction?   

```{r function-show_donors, echo=FALSE, message=FALSE, warning=FALSE}
#' show_donors
#'
#' @description Who are the main donors by country in terms of transaction? 
#' 
#' @param year year to select starting from 2016 - could be one year or a list
#' @param programme_lab A character vector corresponding to the name of the programme.
#' @param iati_identifier_ops A character vector corresponding to the name of the operation.
#' @param ctr_name A character vector corresponding to the name of the country.
#' @param transaction_type_name Transaction type - default is "Incoming Commitment" ,
#'   can also be   "Disbursement", or "Expenditure"  
#' 
#' @import ggplot2
#' @import dplyr
#' @import scales
#' @import unhcrthemes
#'
#' @export 
#'
#' @return  a graph
show_donors <- function(year, 
                        programme_lab = NULL, 
                        iati_identifier_ops = NULL, 
                        ctr_name = NULL,
                        transaction_type_name = "Incoming Commitment"  ) {
  
  ## Check year is after or equal 2016
  
  
  # Check if only one argument is passed 
  if (!is.null(programme_lab) && !is.null(iati_identifier_ops)) {
    stop("Please pass only one of the arguments programme_lab or iati_identifier_ops.")
  } else if (!is.null(programme_lab) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments programme_lab or ctr_name.")
  } else if (!is.null(iati_identifier_ops) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments iati_identifier_ops or ctr_name.")
  }
  
  df <-  iati::dataTransaction |> 
         dplyr::left_join(iati::dataActivity, by= c("iati_identifier"))  
  
  ## Filtering
  if (!is.null(programme_lab)) {
    thisprogramme_lab <- programme_lab
    thisyear <-  year
    thistransaction_type_name <-  transaction_type_name
    df <- df |> 
      # levels(as.factor(df$programmme_lab))
      dplyr::filter( programmme_lab == thisprogramme_lab &
            year >= thisyear & 
             transaction_type_name ==  thistransaction_type_name)
  } else if (!is.null(iati_identifier_ops)) {
    thisiati_identifier_ops <- iati_identifier_ops
    thisyear <-  year
    thistransaction_type_name <-  transaction_type_name
    df <- df |> 
      dplyr::filter(iati_identifier_ops == thisiati_identifier_ops &
            year >= thisyear & 
             transaction_type_name ==  thistransaction_type_name)
  } else if (!is.null(ctr_name)) {
    thisctr_name <- ctr_name
    thisyear <-  year
    thistransaction_type_name <-  transaction_type_name
    df <- df |> 
      dplyr::filter( ctr_name == thisctr_name &
            year >= thisyear & 
             transaction_type_name ==  thistransaction_type_name)
  }
   
 
  
  df1 <- df |> 
    dplyr::group_by(year, provider_org_type_name) |>
    dplyr::summarise( transaction_value_USD = sum(transaction_value_USD , na.rm = TRUE)) |>
    dplyr::mutate(provider_org_type_name = as.character(provider_org_type_name) )  |>
    dplyr::mutate(provider_org_type_name = as.factor(provider_org_type_name) ) 
  
  
    ## case there's no data at all
    if( nrow(df1) == 0) {
      info <-  paste0("No ", transaction_type_name, "\n  recorded   in ", 
                              programme_lab, ctr_name,iati_identifier_ops, " for year: ", year)
      p <- ggplot2::ggplot() +  
                     ggplot2::annotate("text",  x = 1, y = 1, size = 12,
                                          label = info ) +  
                     ggplot2::theme_void()
          
    } else if(nrow(df1)> 0) {
      
      
     p <- df1 |> 
    #  dplyr::filter(transaction_value_USD  <= 1000000 & transaction_value_USD  > 1000) |> 
      ggplot2::ggplot(ggplot2::aes(y = transaction_value_USD ,
                 x =  year,
                 fill = provider_org_type_name)) +
      ggplot2::geom_bar(alpha = 0.9, stat = "identity") +
      ggplot2::scale_fill_viridis_d(option = "inferno", na.value = "grey50") +
      ggplot2::scale_y_continuous(
        expand = ggplot2::expansion(mult = c(0, .1)),
        labels = scales::label_number(scale_cut = scales::cut_short_scale())  ) +
    #  scale_x_continuous(labels = scales::label_number(scale_cut = cut_short_scale())) +
     # ggplot2::facet_wrap(~ trans_year) +
      unhcrthemes::theme_unhcr(grid = "Y", axis = "X", axis_title = "X", font_size = 18)+
      ggplot2::labs(
        title = paste0(transaction_type_name," (in USD)"),
        subtitle = paste0("Recorded in ", programme_lab, ctr_name,iati_identifier_ops, " since ", year,""),
        x = "",
        y = "",
        caption = "Source: Data published by UNHCR as part of the International Aid Transparency Initiative (IATI)" ) 
           }
 
  return(p)
}
```


```{r examples-show_donors, message=FALSE, warning=FALSE, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center",  out.width = "90%"}
knitr::kable(iati::dataTransaction |>
                dplyr::select( transaction_type_name, transaction_type_description) |>
                dplyr::distinct() )
show_donors(year = 2022,
           programme_lab = "The Americas",
           transaction_type_name = "Incoming Commitment" )
show_donors(year = 2018,
           ctr_name = "Brazil",
           transaction_type_name = "Incoming Commitment" )
show_donors(year = 2018,
           programme_lab = "Brazil",
           transaction_type_name = "Disbursement" )
show_donors(year = 2018,
           programme_lab = "Brazil",
           transaction_type_name = "Expenditure" )
```

```{r tests-show_donors}
test_that("show_donors works", {
  expect_true(inherits(show_donors, "function")) 
})
```

## show_top_donors
    
```{r function-show_top_donors}
#' show_top_donors
#'
#' @description Who are the main donors by country in terms of transaction? 
#' 
#' @param year year to select starting from 2016 - could be one year or a list
#' @param programme_lab A character vector corresponding to the name of the programme.
#' @param iati_identifier_ops A character vector corresponding to the name of the operation.
#' @param ctr_name A character vector corresponding to the name of the country. 
#' @param top_n top n donors to show - the rest being lumped together
#' 
#' @import ggplot2
#' @import dplyr
#' @import scales
#' @import unhcrthemes
#'
#' @export 
#'
#' @return  a graph
show_top_donors <- function(year, 
                        programme_lab = NULL, 
                        iati_identifier_ops = NULL, 
                        ctr_name = NULL, 
                        top_n = 5) {
  
  ## Check year is after or equal 2016
  
  
  # Check if only one argument is passed 
  if (!is.null(programme_lab) && !is.null(iati_identifier_ops)) {
    stop("Please pass only one of the arguments programme_lab or iati_identifier_ops.")
  } else if (!is.null(programme_lab) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments programme_lab or ctr_name.")
  } else if (!is.null(iati_identifier_ops) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments iati_identifier_ops or ctr_name.")
  }
  
  df <-  iati::dataTransaction |> 
         dplyr::left_join(iati::dataActivity, by= c("iati_identifier"))  
  
  ## Filtering
  if (!is.null(programme_lab)) {
    thisprogramme_lab <- programme_lab
    thisyear <-  year 
    df <- df |> 
      # levels(as.factor(df$programmme_lab))
      dplyr::filter( programmme_lab == thisprogramme_lab &
            year == thisyear & 
             transaction_type_name ==  "Incoming Commitment")
  } else if (!is.null(iati_identifier_ops)) {
    thisiati_identifier_ops <- iati_identifier_ops
    thisyear <-  year 
    df <- df |> 
      dplyr::filter(iati_identifier_ops == thisiati_identifier_ops &
            year == thisyear & 
             transaction_type_name ==  "Incoming Commitment")
  } else if (!is.null(ctr_name)) {
    thisctr_name <- ctr_name
    thisyear <-  year 
    df <- df |> 
      dplyr::filter( ctr_name == thisctr_name &
            year == thisyear & 
             transaction_type_name == "Incoming Commitment")
  }
   
   
  df2 <- df |>
    dplyr::group_by(year, transaction_provider_org) |>
    dplyr::summarise( transaction_value_USD = sum(transaction_value_USD , na.rm = TRUE)) |>
    dplyr::mutate( transaction_provider_org = as.character(transaction_provider_org) )  |>
    dplyr::mutate( transaction_provider_org = as.factor(transaction_provider_org) )  |>
    dplyr::mutate( transaction_provider_org = forcats::fct_lump_n(
        f = transaction_provider_org,
        n = top_n,  #### Parameter
        w = transaction_value_USD,
        other_level = 'Other Partners',
        ties.method = "last")    ) |>
    dplyr::group_by(year, transaction_provider_org) |>
    dplyr::summarise( transaction_value_USD = sum(transaction_value_USD , na.rm = TRUE)) |>
    dplyr::mutate(transaction_provider_org = as.character(transaction_provider_org) )  |>
    dplyr::mutate(transaction_provider_org = as.factor(transaction_provider_org) )
  
  #levels(as.factor(df2$transaction_provider_org))

  
 p <- df2 |> 
#  dplyr::filter(transaction_value_USD  <= 1000000 & transaction_value_USD  > 1000) |> 
  ggplot2::ggplot(ggplot2::aes(y = transaction_value_USD ,
             x = stats::reorder( transaction_provider_org, transaction_value_USD) )) +
  ggplot2::geom_bar(alpha = 0.9, stat = "identity", fill = "#0072BC") +
  ggplot2::coord_flip() +
  ggplot2::scale_y_continuous(
    expand = ggplot2::expansion(mult = c(0, .1)),
    labels = scales::label_number(scale_cut = scales::cut_short_scale())  ) +
#  scale_x_continuous(labels = scales::label_number(scale_cut = cut_short_scale())) +
 # ggplot2::facet_wrap(~ trans_year) +
  unhcrthemes::theme_unhcr(grid = "X", axis = "X", axis_title = "X", font_size = 18)+
  ggplot2::labs(
    title = paste0("Top ",top_n ," donors (in USD)"),
    subtitle = paste0("Incoming Commitment Recorded in ", programme_lab, ctr_name,iati_identifier_ops, " | ", year,""),
    x = "",
    y = "",
    caption = "Source: Data published by UNHCR as part of the International Aid Transparency Initiative (IATI)" ) 
 
  return(p)
}
```
  
```{r example-show_top_donors, message=FALSE, warning=FALSE, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center",  out.width = "90%"}
show_top_donors(year = 2022,
           ctr_name = "Brazil", 
           top_n = 5)
show_top_donors(year = 2020,
           ctr_name = "Brazil", 
           top_n = 10)
```
  
```{r tests-show_top_donors}
test_that("show_top_donors works", {
  expect_true(inherits(show_top_donors, "function")) 
})
```
  



## show_earmarking

 *  Whats the breakdown of __Earmarking Type__ (Un-earmarked, Tightly earmarked, etc.) from Donor Funds by Year?  
 
    
```{r function-show_earmarking}
#' Title
#' 
#' @description Whats the breakdown of Earmarking Type (Un-earmarked, Tightly earmarked, etc.) \
#'  from Donor Funds by Year?  
#'  Where possible, UNHCR prefers to receive unearmarked funds, as this allows the agency 
#'  greater flexibility in allocating its resources as new needs emerge during the course of the year. 
#'  Should that not be possible, funds can also be softly earmarked. This could mean funds that 
#'  can be spent anywhere within a region or for a particular situation (for example, funds that have 
#'  to be spent to assist refugees from Syria, but which can be spent in any country hosting such 
#'  refugees). Earmarked funds would be a contribution that corresponds to a specific country but 
#'  can be spent on anything within that operations programme. Finally, tightly earmarked funds 
#'  are those that specify an activity or a population within a countrys programme.
#'  
#'  UNHCR charges an ISC -  Indirect Support Costs - rate of 6.5% on all of its earmarked contributions.
#'   This covers management and administration  costs at HQ and programme support costs 
#'   incurred at HQ and Regional Bureaux. 
#' 
#' @param year A numeric value corresponding to the first year of focus until the most recent year within the dataset.
#' @param programme_lab A character vector corresponding to the name of the programme.
#' @param iati_identifier_ops A character vector corresponding to the name of the operation.
#' @param ctr_name A character vector corresponding to the name of the country.
#' 
#' @import ggplot2
#' @import dplyr
#' @import scales
#' @import unhcrthemes
#'
#' @export 
#' @return  a graph
show_earmarking <- function(year, 
                        programme_lab = NULL, 
                        iati_identifier_ops = NULL, 
                        ctr_name = NULL  ) {
  
  
  # Check if only one argument is passed 
  if (!is.null(programme_lab) && !is.null(iati_identifier_ops)) {
    stop("Please pass only one of the arguments programme_lab or iati_identifier_ops.")
  } else if (!is.null(programme_lab) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments programme_lab or ctr_name.")
  } else if (!is.null(iati_identifier_ops) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments iati_identifier_ops or ctr_name.")
  }
  
  df <-  iati::dataTransaction |> 
         dplyr::left_join(iati::dataActivity, by= c("iati_identifier"))  
  
  if (!is.null(programme_lab)) {
    thisprogramme_lab <- programme_lab
    thisyear <-  year 
    df <- df |> 
      # levels(as.factor(df$programmme_lab))
      dplyr::filter( programmme_lab == thisprogramme_lab &
            year >= thisyear & 
             transaction_type_name ==  "Incoming Commitment")
  } else if (!is.null(iati_identifier_ops)) {
    thisiati_identifier_ops <- iati_identifier_ops
    thisyear <-  year 
    df <- df |> 
      dplyr::filter(iati_identifier_ops == thisiati_identifier_ops &
            year >= thisyear & 
             transaction_type_name ==  "Incoming Commitment")
  } else if (!is.null(ctr_name)) {
    thisctr_name <- ctr_name
    thisyear <-  year 
    df <- df |> 
      dplyr::filter( ctr_name == thisctr_name &
            year >= thisyear & 
             transaction_type_name ==  "Incoming Commitment")
  }
  # levels(as.factor(df$earmarking_name)) 
  
  df2 <- df |> 
    dplyr::group_by(year, earmarking_name) |>
    dplyr::summarise( transaction_value_USD = sum(transaction_value_USD , na.rm = TRUE)) |>
    dplyr::mutate(earmarking_name = as.character(earmarking_name) )  |>
    dplyr::mutate(earmarking_name = as.factor(earmarking_name) ) 
  
 
  cols_earmarking_name <- c("Earmarked" = "#e1cc0d",
                    "Softly Earmarked" = "#0072bc", 
                    "Tightly Earmarked" = "#ef4a60", 
                    "Unearmarked" = "#00b398" )
  
 p <- df2 |> 
#  dplyr::filter(transaction_value_USD  <= 1000000 & transaction_value_USD  > 1000) |> 
  ggplot2::ggplot(ggplot2::aes(y = transaction_value_USD ,
             x =  year,
             fill = earmarking_name)) +
  ggplot2::geom_bar(alpha = 0.9, stat = "identity") +
  #ggplot2::scale_fill_viridis_d(option = "inferno", na.value = "grey50") +
  ggplot2::scale_fill_manual(values = cols_earmarking_name,
                      drop = TRUE,
                      limits = force,
                      na.value = "grey50") +
  ggplot2::scale_y_continuous(
    expand = ggplot2::expansion(mult = c(0, .1)),
    labels = scales::label_number(scale_cut = scales::cut_short_scale())  ) +
#  scale_x_continuous(labels = scales::label_number(scale_cut = cut_short_scale())) +
 # ggplot2::facet_wrap(~ trans_year) +
  unhcrthemes::theme_unhcr(grid = "Y", axis = "X", axis_title = "X", font_size = 18)+
  ggplot2::labs(
    title = paste0("Commitment vs Earmarking (in USD)"),
    subtitle = paste0("Recorded in ", programme_lab, ctr_name,iati_identifier_ops, " since ", year,""),
    x = "",
    y = "",
    caption = "Source: Data published by UNHCR as part of the International Aid Transparency Initiative (IATI)" ) 
 
  return(p) 
}
```
  
```{r example-show_earmarking, message=FALSE, warning=FALSE, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center",  out.width = "90%"}
knitr::kable(iati::dataTransaction |>
                dplyr::select(earmarking_name, earmarking_description)  |>
                dplyr::distinct() |>
                dplyr::filter(!(is.na(earmarking_name))))
show_earmarking(year = 2018,  
             ctr_name = "Brazil")
```
  
```{r tests-show_earmarking}
test_that("show_earmarking works", {
  expect_true(inherits(show_earmarking, "function")) 
})
```
  

## show_contributions
    
```{r function-show_contributions}
#' Title
#' 
#' @description Whats the breakdown by contribution Type (Un-earmarked, Tightly earmarked, etc.) from Donor Funds by Year?  
#' 
#' @param year A numeric value corresponding to the first year of focus until the most recent year within the dataset.
#' @param programme_lab A character vector corresponding to the name of the programme.
#' @param iati_identifier_ops A character vector corresponding to the name of the operation.
#' @param ctr_name A character vector corresponding to the name of the country.
#' 
#' @import ggplot2
#' @import dplyr
#' @import scales
#' @import unhcrthemes
#'
#' @export 
#' @return  a graph
show_contributions <- function(year, 
                        programme_lab = NULL, 
                        iati_identifier_ops = NULL, 
                        ctr_name = NULL  ) {
  
  
  # Check if only one argument is passed 
  if (!is.null(programme_lab) && !is.null(iati_identifier_ops)) {
    stop("Please pass only one of the arguments programme_lab or iati_identifier_ops.")
  } else if (!is.null(programme_lab) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments programme_lab or ctr_name.")
  } else if (!is.null(iati_identifier_ops) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments iati_identifier_ops or ctr_name.")
  }
  
  df <-  iati::dataTransaction |> 
         dplyr::left_join(iati::dataActivity, by= c("iati_identifier"))  
  
  if (!is.null(programme_lab)) {
    thisprogramme_lab <- programme_lab
    thisyear <-  year 
    df <- df |> 
      # levels(as.factor(df$programmme_lab))
      dplyr::filter( programmme_lab == thisprogramme_lab &
            year >= thisyear & 
             transaction_type_name ==  "Incoming Commitment")
  } else if (!is.null(iati_identifier_ops)) {
    thisiati_identifier_ops <- iati_identifier_ops
    thisyear <-  year 
    df <- df |> 
      dplyr::filter(iati_identifier_ops == thisiati_identifier_ops &
            year >= thisyear & 
             transaction_type_name ==  "Incoming Commitment")
  } else if (!is.null(ctr_name)) {
    thisctr_name <- ctr_name
    thisyear <-  year 
    df <- df |> 
      dplyr::filter( ctr_name == thisctr_name &
            year >= thisyear & 
             transaction_type_name ==  "Incoming Commitment")
  }
   
  df2 <- df |> 
    dplyr::group_by(year, aid_type1_name) |>
    dplyr::summarise( transaction_value_USD = sum(transaction_value_USD , na.rm = TRUE)) |>
    dplyr::mutate(aid_type1_name = as.character(aid_type1_name) )  |>
    dplyr::mutate(aid_type1_name = as.factor(aid_type1_name) ) 
  
 p <- df2 |> 
#  dplyr::filter(transaction_value_USD  <= 1000000 & transaction_value_USD  > 1000) |> 
  ggplot2::ggplot(ggplot2::aes(y = transaction_value_USD ,
             x =  year,
             fill = aid_type1_name)) +
  ggplot2::geom_bar(alpha = 0.9, stat = "identity") +
  ggplot2::scale_fill_viridis_d(option = "inferno", na.value = "grey50") +
  ggplot2::scale_y_continuous(
    expand = ggplot2::expansion(mult = c(0, .1)),
    labels = scales::label_number(scale_cut = scales::cut_short_scale())  ) +
#  scale_x_continuous(labels = scales::label_number(scale_cut = cut_short_scale())) +
 # ggplot2::facet_wrap(~ trans_year) +
  unhcrthemes::theme_unhcr(grid = "Y", axis = "X", axis_title = "X", font_size = 18)+
  ggplot2::labs(
    title = paste0("Commitment vs Contribution type (in USD)"),
    subtitle = paste0("Recorded in ", programme_lab, ctr_name,iati_identifier_ops, " since ", year,""),
    x = "",
    y = "",
    caption = "Source: Data published by UNHCR as part of the International Aid Transparency Initiative (IATI)" ) 
 
  return(p) 
}
```
  
```{r example-show_contributions, message=FALSE, warning=FALSE, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center",  out.width = "90%"}
knitr::kable(iati::dataTransaction |>
                dplyr::select(aid_type1_name, aid_type1_description)  |>
                dplyr::distinct() |>
                dplyr::filter(!(is.na(aid_type1_name))))
show_contributions(year = 2018, 
                   ctr_name = "Brazil") 
show_contributions(year = 2018, 
                   programme_lab = "The Americas") 
```
  
```{r tests-show_contributions}
test_that("show_contributions works", {
  expect_true(inherits(show_contributions, "function")) 
})
```
  
# Using `iati::dataParticipating_org`

## Show partnership

 
 *  How __organisations partner together__?   
 

```{r function-show_partnership, echo=FALSE, message=FALSE, warning=FALSE}
#' show_partnership
#' 
#' @description How organisations partner together? 
#'
#' @param year A numeric value corresponding to the year to be displayed
#' @param programme_lab A character vector corresponding to the name of the programme.
#' @param iati_identifier_ops A character vector corresponding to the name of the operation.
#' @param ctr_name A character vector corresponding to the name of the country.
#' 
#' @import ggplot2
#' @import dplyr
#' @import scales
#' @import unhcrthemes
#'
#' @export 
#' @return  a graph
show_partnership <- function( year, 
                        programme_lab = NULL, 
                        iati_identifier_ops = NULL, 
                        ctr_name = NULL  ) {
  
  
  # Check if only one argument is passed 
  if (!is.null(programme_lab) && !is.null(iati_identifier_ops)) {
    stop("Please pass only one of the arguments programme_lab or iati_identifier_ops.")
  } else if (!is.null(programme_lab) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments programme_lab or ctr_name.")
  } else if (!is.null(iati_identifier_ops) && !is.null(ctr_name)) {
    stop("Please pass only one of the arguments iati_identifier_ops or ctr_name.")
  }
  
  df <-  iati::dataParticipating_org |> 
         dplyr::left_join(iati::dataActivity, by= c("iati_identifier"))  
  
  if (!is.null(programme_lab)) {
    thisprogramme_lab <- programme_lab
    thisyear <-  year
    df <- df |> 
      # levels(as.factor(df$programmme_lab))
      dplyr::filter( programmme_lab == thisprogramme_lab &
            year == thisyear )
  } else if (!is.null(iati_identifier_ops)) {
    thisiati_identifier_ops <- iati_identifier_ops
    thisyear <-  year
    df <- df |> 
      dplyr::filter(iati_identifier_ops == thisiati_identifier_ops &
            year == thisyear )
  } else if (!is.null(ctr_name)) {
    thisctr_name <- ctr_name
    thisyear <-  year
    df <- df |> 
      dplyr::filter( ctr_name == thisctr_name &
            year == thisyear )
  }
  
  df2 <- df    |>
    dplyr::select(participating_org_eng, 
                  participating_org_type_name, 
                  participating_org_role_name) |>
     tidyr::pivot_wider(names_from = participating_org_role_name, 
              values_from = participating_org_eng ,
              values_fn = list) |>
    dplyr::select( - Accountable)  |>
    dplyr::rename(Organisation =participating_org_type_name) 
  ## replace null values...
  df2[df2 == 'NULL'] <- as.list(" ")
  
  
  df3 <- df    |>
    dplyr::select(participating_org_eng, 
                  participating_org_type_name, 
                  participating_org_role_name) |>
    #  count(across(everything())) |>
     tidyr::pivot_wider(names_from = participating_org_role_name, 
               values_from = participating_org_eng,
                values_fn = function(x) length(!is.na(x)),
                values_fill = 0)
  
  ##df |> dplyr::select(participating_org_type, participating_org_role ) |> dplyr::distinct()
   
  ## Let's build a table with a participating type as row - role as column -
  # and in the cell the numeber and list of corresponding org.. participating_org_eng
  ## Facet this by year... 
  
  # Dummy data
    # participating_org_type_name <- LETTERS[1:8]
    # participating_org_type_role <- paste0("var", seq(1,4))
    # df <- expand.grid(participating_org_type_name = participating_org_type_name,
    #                   participating_org_type_role = participating_org_type_role)
    # df$count <- runif(32, 0, 5)
  
  
#  p <- df3 |> 
# #  dplyr::filter(transaction_value_USD  <= 1000000 & transaction_value_USD  > 1000) |> 
#   ggplot2::ggplot(ggplot2::aes(x =  participating_org_type_name, 
#                                y = participating_org_type_role , 
#                                fill = count,
#                                label = count)) +
#     
#   ggplot2::geom_tile(alpha = 0.9) +  
#   ggplot2::geom_text( size=2.5)  + 
#   #ggplot2::scale_fill_viridis_c(option = "inferno", na.value = "grey50" ) +
#   ggplot2::scale_fill_gradient2(low = "white" ,
#                        mid = "#FFFFCC",
#                        high = "#075AFF") 
#   unhcrthemes::theme_unhcr(grid =  FALSE, axis = FALSE, axis_title =  TRUE, legend = FALSE)+
#   ggplot2::labs(
#     title = paste0(" Partners"),
#     subtitle = paste0("In ", programme_lab, " recorded since ", year,""),
#     x = "Organisation Type",
#     y = "Organisation Role",
#     caption = "Source: Data published by UNHCR as part of the International Aid Transparency Initiative (IATI)" ) 
 
  p <- knitr::kable( df2  )
  
  return(p)
}
```
 
```{r examples-show_partnership, message=FALSE, warning=FALSE, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center",  out.width = "90%"}
show_partnership(year = 2022,
           ctr_name = "Brazil" ) 
```

```{r tests-show_partnership}
test_that("show_partnership works", {
  expect_true(inherits(show_partnership, "function")) 
})
```

 


# Template

## template_prez
    
```{r function-template_prez}

# usethis::use_rmarkdown_template(
#   template_name = "iati_prez",
#   template_dir = NULL,
#   template_description = "UNHCR IATI",
#   template_create_dir = TRUE
# )


#' Generate a summary powerpoint
#' 
#' @param year A numeric value corresponding to the first year of focus until the most recent year within the dataset.
#' @param ctr_name A character vector corresponding to the name of the country.
#' @param folder folder within your project where to put the generated report. 
#'              Folder will be created if it does not exist
#' 
#' @importFrom unhcrdown pptx_slides
#' @importFrom dplyr filter select pull
#' @importFrom rmarkdown render
#' @importFrom here here
#' 
#' @return nothing the file for the report is generated
#' 
#' @export 
#'
template_prez <- function(year = 2022,
                          ctr_name,   
                          folder = "Prez") {
  
  ## Create the outfolder if it does not exist
  output_dir <- paste0(getwd(),"/",folder)
  if (!dir.exists(output_dir)) {dir.create(output_dir)}
  
  rmarkdown::render(
    system.file("rmarkdown/templates/iati_prez/skeleton/skeleton.Rmd", package = "iati"),
    output_file = here::here(folder, paste0('iati_prez-', ctr_name, '-', year, '.pptx') ),
    params = list(ctr_name = ctr_name, 
                  year = year)  )
}
```
  
```{r example-template_prez}

## generate for one country
# iati::template_prez(year = 2022, 
#                     ctr_name = "Brazil",
#                     folder = "dev/Prez")

# ## Generate for all operation specific region
# region <- "The Americas"
# 
# countries <- iati::dataActivity |> 
#        dplyr::filter( unhcr_region ==  region) |>
#        dplyr::select(ctr_name) |>
#        dplyr::distinct() |>
#        dplyr::pull()
# 
# for ( ctr in countries) {
#     cat(paste0(ctr, "\n"))
#     iati::template_prez(year = 2022, 
#                     ctr_name = ctr,
#                     folder = "dev/Prez")  }
```
  
```{r tests-template_prez}
test_that("template_prez works", {
  expect_true(inherits(template_prez, "function")) 
})
```
  


```{r development-inflate, eval=FALSE}
# Inflate the package

# You're one inflate from paper to box.
# Build your package from this very Rmd using `fusen::inflate()`
# 
# - Verify your `"DESCRIPTION"` file has been updated
# - Verify your function is in `"R/"` directory
# - Verify your test is in `"tests/testthat/"` directory
# - Verify this Rmd appears in `"vignettes/"` directory

# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/dev_unhcr_programme.Rmd", vignette_name = "UNHCR Programme")
```



